\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2014-03-31 introduction.tex
Updated the paper

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is elastic.
Although the timing model with logical clock has worked well for
reactive synchronous/GALS languages in designing discrete systems, there
is a need to introduce real-time since often, implementation models are
in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}. This paper targets
enhancing formal GALS and synchronous languages, by adding real-time
constructs. The real-time constructs speed up a design process by
allowing system designers to explicitly program real-time postponements
within the language itself without need of external resources such as
timers.

@@

\begin{enumerate*}
\item Real-time is specified in the $\mathbb{Q}^{>0}$ domain of numbers,
  i.e., non-negative rational numbers.
% \item We consider the property of \textit{non
%     maximal-parallelism}. \textit{Non-maximal parallelism:} There are
%   not always sufficient resources for processes to execute, so
%   effectively processes are allocated and scheduled with different
%   optimization criteria -- reducing computation time, reducing power
%   consumption, etc. This allocation and scheduling is an integral part
%   of any language compilation and needs to be considered when
%   introducing real-time waits.
\item We are the first, to our knowledge, to allow specification of
  both; exact and non-exact real-time in GALS and synchronous programs.
\item We shed light upon a key insight relating real-time and
  logical-time -- \textit{the resolution of any real-time statement is
    dependent on the worst case logical tick time} -- an aspect that
  seems to have escaped in the current literature on incorporation of
  real-time in synchronous/GALS languages.
\item We \textbf{assume} that real-time analyzable platforms are
	available on which SystemJ programs are executed.
\end{enumerate*}

The rest of the paper is arranged as follows:
Section~\ref{sec:background} gives the background on SystemJ and related
techniques required for the rest of the
paper. Section~\ref{sec:intr-real-time} introduces real-time mechanisms
in the GALS paradigm and describes their compilation into logical
time. Section~\ref{sec:proof-correctness} sketches the correctness
proofs for the introduced
algorithms. Section~\ref{sec:experimental-results} gives the
experimental results for a set of real-time applications. In
Section~\ref{sec:disc-perc-limit} we discuss the advantages and
limitations of the proposed approach. Section~\ref{sec:related-work}
positions this work in relation to other approaches to introducing
real-time in other languages. Finally, we conclude in
Section~\ref{sec:concl-future-work}.

>>>>

Reactive languages~\cite{gber931,amal10} are a class of programming
languages used for designing and implementing reactive systems, which
continuously respond to input from their environment. These languages
have been successfully used in programming a plethora of systems such as
fly-by-wire in Airbus~\cite{eairbus}, security surveillance
systems~\cite{amal121}, etc. Usually these systems also need to meet
real-time constraints imposed by the environment. Yet, these languages
do not support describing real-time statements as first class language
constructs.  For example, one cannot describe a simple real-time delay
(postponement) of an operation for 0.2 ms. These languages are based on
formal semantics, essential for correct by construction code generation
and formally verifying functional properties of developed programs, but
leave nonfunctional properties such as timing behavior as an
implementation detail~\cite{boldt07}. Arguably, rightly so, because
physical time cannot be incorporated without information about the
underlying execution platform.  But, one can still reason in terms of
logical time. These languages support discrete logical clock rather than
a discrete physical (real-time) clock. The real-time period of the
discrete logical clock (also referred to as a logical tick) is not fixed
and it is determined by the speed of computation of the program for
different input signals. Unlike a discrete physical clock, which has
fixed real-time period, the period of the logical clock is elastic.
Although the timing model with logical clock has worked well for
reactive synchronous/GALS languages in designing discrete systems, there
is a need to introduce real-time since often, implementation models are
in the continuous or discrete real-time
domain~\cite{DBLP:journals/pieee/SifakisTY03}. This paper targets
enhancing the expressiveness of formal GALS and synchronous languages by
adding real-time constructs. The real-time constructs speed up the
design process by allowing system designers to explicitly program
real-time control logic within the language itself without relying on
external resources such as timers.

@@

\begin{enumerate*}
\item Real-time is specified in the $\mathbb{Q}^{>0}$ domain of numbers,
  i.e., non-negative rational numbers.
% \item We consider the property of \textit{non
%     maximal-parallelism}. \textit{Non-maximal parallelism:} There are
%   not always sufficient resources for processes to execute, so
%   effectively processes are allocated and scheduled with different
%   optimization criteria -- reducing computation time, reducing power
%   consumption, etc. This allocation and scheduling is an integral part
%   of any language compilation and needs to be considered when
%   introducing real-time waits.
\item We are the first, to our knowledge, to allow specification of
  both; exact and non-exact real-time in GALS and synchronous programs.
\item We shed light upon a key insight relating real-time and
  logical-time -- \textit{the resolution of any real-time statement is
    dependent on the worst case logical tick time} -- an aspect that
  seems to have escaped in the current literature on incorporation of
  real-time in synchronous/GALS languages.
\end{enumerate*}

All aforementioned contributions hold under a single assumption that
real-time analyzable platforms are available. The rest of the paper is
arranged as follows: Section~\ref{sec:background} gives the background
on SystemJ and related techniques required for the rest of the paper.
Section~\ref{sec:intr-real-time} introduces real-time mechanisms in the
GALS paradigm and describes their compilation into logical time.
Section~\ref{sec:proof-correctness} sketches the correctness proofs for
the introduced algorithms. Section~\ref{sec:experimental-results} gives
the experimental results for a set of real-time applications. In
Section~\ref{sec:disc-perc-limit} we discuss the advantages and
limitations of the proposed approach. Section~\ref{sec:related-work}
positions this work in relation to other approaches to introducing
real-time in other languages. Finally, we conclude in
Section~\ref{sec:concl-future-work}.

### 2014-03-31 motivation.tex
Updated the paper

The timing diagram, Figure~\ref{dd:b}, shows that the
\texttt{wait\_atleast} statement waits for a \textit{at least} 10
seconds, but unlike \texttt{wait\_inbetween} there is no upper
bound. The statement following the \texttt{wait\_atleast} statement is
executed after a finite countable, but unbounded postponement. Such a
statement is useful for programming low priority tasks.

>>>>

The timing diagram, Figure~\ref{dd:b}, shows that the
\texttt{wait\_atleast} statement waits for a \textit{at least} 10
seconds, but unlike \texttt{wait\_inbetween} there is no upper bound.
For example in Figure~\ref{dd:b} program can proceed to the next
statement at 11 seconds. The statement following the
\texttt{wait\_atleast} statement is executed after a finite countable,
but unbounded postponement. Such a statement is useful for programming
low priority tasks.
